The Power of Unbiased Recursive Partitioning:\\ A Unifying View of CTree, MOB, and GUIDE

### 2019-05-31 pkg/partykit/inst/guideliketest/draft/draft.Rnw
adapted tab:combinations_appendix
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2598 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: f303946b2469daa1cfbec4e7ee3139deccdc0cf8

\begin{table}[h!]
\centering
\begin{tabular}{ l l l l }
\hline 
Testing Strategy  & Residuals/Scores   & Binarization & Categorization \\
\hline
GUIDE             & residuals          & yes          & cat \\
MOB+bin+res       & residuals          & yes          & max \\
CTree+bin+res     & residuals          & yes          & lin \\
MOB+cat+res       & residuals          & no           & cat \\
MOB+res           & residuals          & no           & max \\
CTree+res         & residuals          & no           & lin \\
GUIDE+scores      & scores             & yes          & cat \\
MOB+bin           & scores             & yes          & max \\
CTree+bin         & scores             & yes          & lin \\
MOB+cat           & scores             & no           & cat \\
MOB               & scores             & no           & max \\
CTree             & scores             & no           & lin \\
\hline
\end{tabular}
\caption{Testing strategies applied (representing the 12 combinations
of building blocks).
\label{tab:combinations_appendix}}
\end{table}

>>>>

\begin{table}[h!]
\centering
\begin{tabular}{ l l l l l}
\hline\noalign{\smallskip} 
Residuals/Scores   & Dichotomization & Categorization & \multicolumn{2}{l}{Via testing strategy}\\
\noalign{\smallskip}\hline\noalign{\smallskip}
residuals	   & yes	     & cat            & GUIDE & {(default)}\\
residuals	   & yes	     & max            & MOB   & {(with modifications)}\\
residuals	   & yes	     & lin            & CTree & {(with modifications)}\\
residuals	   & no 	     & cat            & MOB   & {(with modifications)}\\
residuals	   & no 	     & max            & MOB   & {(with modifications)}\\
residuals	   & no 	     & lin            & CTree & {(with modifications)}\\
scores  	   & yes	     & cat            & GUIDE & {(with modifications)}\\
scores  	   & yes	     & max            & MOB   & {(with modifications)}\\
scores  	   & yes	     & lin            & CTree & {(with modifications)}\\
scores  	   & no 	     & cat            & MOB   & {(with modifications)}\\
scores  	   & no 	     & max            & MOB   & {(default)}\\
scores  	   & no 	     & lin            & CTree & {(default)}\\
\noalign{\smallskip}\hline
\end{tabular}
\caption{Testing strategies applied for all 12 factorial combinations of the building blocks.
For each combination one of the three testing strategies CTree/MOB/GUIDE is applied,
possibly after modifying the assessed variables as indicated (i.e., dichotomized or categorized).
\label{tab:combinations_appendix}}
\end{table}
